A non-additive generalization of probability theory \\for quantum mechanics and beyond

### 2025-07-30 Articles/2024-NonAdditiveProbability/NonAdditiveProbability.tex
NonAdditiveProbability: Plot Choquet integrand in TikZ
Replace the matplotlib code with TikZ code.

To recap, we have
\begin{equation}
	\frcap_{\ens[o]}(A(s))=
	\begin{cases}
		1 & \text{if } s\leq \frac{1}{2} a + \frac{1}{2} b\\
		\frac{1}{2} \frac{b - a}{s-a} & \text{if } \frac{1}{2} a + \frac{1}{2} b < s \leq b\\
		0 & \text{if } s > b.
	\end{cases}
\end{equation}
\begin{figure}[H]
	\centering
	\includegraphics[width=0.4\textwidth]{ChoquetPlot.png}
	\caption{The integrand $\frcap_{\ens[o]}(A(s))$ as a function of $s$.}
\end{figure}
We can now calculate the integral
\begin{equation}
	\begin{aligned}
		(C)&\int F d\frcap_{\ens[o]} := 
		\int_{-\infty}^0
		(\frcap_{\ens[o]} (A(s))-\frcap_{\ens[o]}(X))\, ds \\
		&+
		\int^\infty_0
		\frcap_{\ens[o]} (A(s))\, ds \\
		&= \int_{-\infty}^0 (1 - 1)ds + \int_{0}^{\frac{1}{2} a + \frac{1}{2} b}  1 ds \\
		&+ \int_{\frac{1}{2} a + \frac{1}{2} b}^{b}  \frac{1}{2} \frac{b - a}{s-a} ds + \int_{b}^{\infty} 0 ds \\
		&=\left[s\right]_{0}^{\frac{1}{2} a + \frac{1}{2} b}
		+ \frac{1}{2}\left(b - a\right)\left[\ln (s - a)\right]_{\frac{1}{2} a + \frac{1}{2} b}^{b} \\
		&= \frac{1}{2} a + \frac{1}{2} b + \frac{1}{2}\left(b - a\right)\left[\ln (b - a)\right. \\
		&+\left. \ln \left(\frac{1}{2} a + \frac{1}{2} b - a\right) \right] \\
		&= \frac{1}{2} a + \frac{1}{2} b + \frac{1}{2}\left(b - a\right)\ln (2)
	\end{aligned}
\end{equation}

>>>>

To recap, we have
\begin{equation}
	\frcap_{\ens[o]}(A(s))=
	\begin{cases}
		1 & \text{if } s\leq \frac{1}{2} a + \frac{1}{2} b\\
		\frac{1}{2} \frac{b - a}{s-a} & \text{if } \frac{1}{2} a + \frac{1}{2} b < s \leq b\\
		0 & \text{if } s > b.
	\end{cases}
\end{equation}
\begin{figure}[H]
	\centering
	\newcommand{\ticklength}{0.03}
	\begin{tikzpicture}[scale=3]
		% axes
		\draw[->] (0, 0) -- (1.3, 0);
		\draw (0, 0) node[left] {$0$} -- +(-\ticklength, 0) (0, 0.5) node[left] {$1/2$} -- +(-\ticklength, 0) (0, 1) node[left] {$1$} -- +(-\ticklength, 0);
		\draw[->] (0, 0) -- (0, 1.1);
		\draw (0, 0) node[below] {$a$} -- +(0, -\ticklength) (0.5, 0) node[below] {$1/2(a+b)$} -- +(0, -\ticklength) (1, 0) node[below] {$b$} -- +(0, -\ticklength);
		% cases s <= 1/2(a+b) and 1/2(a+b) < s <= b
		\draw[thick, blue, domain=0.5:1, samples=200] (0, 1) --plot (\x, {0.5/\x});
		% mark discontinuity
		\filldraw (1, 0.5) circle (0.02cm);
		\draw (1, 0) circle (0.02cm);
		% case s > b
		\draw[thick, blue] (1, 0) -- (1.2, 0);
	\end{tikzpicture}
	\caption{The integrand $\frcap_{\ens[o]}(A(s))$ as a function of $s$.}
\end{figure}
We can now calculate the integral
\begin{equation}
	\begin{aligned}
		(C)&\int F d\frcap_{\ens[o]} := 
		\int_{-\infty}^0
		(\frcap_{\ens[o]} (A(s))-\frcap_{\ens[o]}(X))\, ds \\
		&+
		\int^\infty_0
		\frcap_{\ens[o]} (A(s))\, ds \\
		&= \int_{-\infty}^0 (1 - 1)ds + \int_{0}^{\frac{1}{2} a + \frac{1}{2} b}  1 ds \\
		&+ \int_{\frac{1}{2} a + \frac{1}{2} b}^{b}  \frac{1}{2} \frac{b - a}{s-a} ds + \int_{b}^{\infty} 0 ds \\
		&=\left[s\right]_{0}^{\frac{1}{2} a + \frac{1}{2} b}
		+ \frac{1}{2}\left(b - a\right)\left[\ln (s - a)\right]_{\frac{1}{2} a + \frac{1}{2} b}^{b} \\
		&= \frac{1}{2} a + \frac{1}{2} b + \frac{1}{2}\left(b - a\right)\left[\ln (b - a)\right. \\
		&+\left. \ln \left(\frac{1}{2} a + \frac{1}{2} b - a\right) \right] \\
		&= \frac{1}{2} a + \frac{1}{2} b + \frac{1}{2}\left(b - a\right)\ln (2)
	\end{aligned}
\end{equation}
